Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-12-08 doc/manuscript/ESSDmanuscript.Rmd
Update ESSDmanuscript.Rmd

@@

  - present calculations of all variables that would be useful to IPCC. EFDB requires that data in the database be presented in the original article, and as such cannot accept subsequent calculations. For example, if aboveground biomass and total biomass are presented, but root biomass is not presented, root biomass cannot be subsequently calculated and sent to EFDB.

>>>>

We are currently in a climate crisis and as we seek to find answers climate data is increasingly important.**something about climate change and freenhouse gasses** The influence the forests have on asmosphereic carbon has made forest data increasingly valuable.

@@

  - present calculations of all variables that would be useful to IPCC. EFDB requires that data in the database be presented in the original article, and as such cannot accept subsequent calculations. For example, if aboveground biomass and total biomass are presented, but root biomass is not presented, root biomass cannot be subsequently calculated and sent to EFDB. Similarly, fine and coarse root biomass can't be summed; soil carbon can't be summed across depth increments, etc.
